\LARGE \bf Explicit Knowledge and the Deliberative Layer: Lessons Learned

### 2013-07-09 paper.tex
IROS review: clarify/refocused conclusion

\subsection{Knowledge-oriented architecture}

@@

    \item{The first two points enable both a loosely-coupled architecture where
    modules can very easily be removed or replaced by other ones as long as
    they share the same semantics (modules are defined by the knowledge they
    produce),}

    \item{and a \emph{symbolic}, reactive, event-driven approach to robot control.
    By managing events at the same level as the reasoner, we take full
    advantage of the inference abilities of {\sc Oro} to trigger events whose
    \texttt{true} conditions can be inferred.}

@@

We believe that this \emph{knowledge-oriented} approach has a strong potential
not only to enable rich human-robot interaction, but also as a broader approach
to information alignment and fusion in complex robotic systems.

\subsection{Three perspectives on knowledge manipulation for robots}

We conclude this article with three different perspectives on the knowledge-oriented
techniques we have presented here: first, the \emph{architect perspective}:
what are the pro and cons of our approach from an engineer's point of view. Then,
the \emph{logician perspective}: does the promise of automated reasoning for
robots really comes to fruition with ontologies? And finally the
\emph{cognitician perspective} or how explicit knowledge manipulation endows
our robots with new cognitive capabilities.

\subsubsection{The Architect view: loose coupling and modalities merging}

@@

\subsubsection{The Logician view: the importance of trivial inferences}

@@

\subsubsection{The Cognitician view: palpable knowledge and semantic thinking}

@@

One of the difficult challenge of cognitive robotics, however, is to overcome
the relative isolation of each of these communities, to build an embodied
agent, able to autonomously interact.

In this respect, our main contribution is to propose a critical look at a
viable robotic architecture that covers many of the facets of cognitive
robotics and that is actually deployed on several robots.

And if we had a single ``lesson'' to retain, it would likely be that one:
shifting from a robotic system design based on \emph{modules and APIs} to a
system based on \emph{modules and human-level semantic interfaces} has been the
main facilitator both for glueing together deliberative heterogeneous modules
in a meaningful way, and quickly developing new upper-cognition abilities,
including natural dialogue and theory of mind.

>>>>

@@

    \item{The first two points enable a loosely-coupled architecture where
    modules can very easily be removed or replaced by other ones as long as
    they share the same semantics (modules are defined by the knowledge they
    produce),}

    \item{We adopt a \emph{symbolic}, reactive, event-driven approach to robot control.
    By managing events at the same level as the reasoner, we take full
    advantage of the inference abilities of {\sc Oro} to trigger events whose
    \texttt{true} conditions can be inferred.}

@@

Those items are not new \emph{per se}. It seems however interesting to
underline the shift of focus this implies during the design and integration
phases. We can adopt three perspectives to discuss the techniques we have
presented here: first, the \emph{architect perspective}: what are the pro and
cons of our approach from an engineer's point of view. Then, the \emph{logician
perspective}: does the promise of automated reasoning for robots really comes
to fruition with ontologies? And finally the \emph{cognitician perspective} or
how explicit knowledge manipulation endows our robots with new cognitive
capabilities.

\subsection{The Architect view: loose coupling and modalities merging}

@@

\subsection{The Logician view: the importance of trivial inferences}

@@

\subsection{The Cognitician view: palpable knowledge and semantic thinking}

@@

One of the difficult challenge of cognitive robotics, however, is to overcome
the relative isolation of each of these communities to build an autonomous
embodied agent, able to interact with humans. This contribution modestly offers
a critical look at one instance of such a ``real-world'' robotic architecture,
that tackles several of the facets of cognitive robotics.

If we had a single ``lesson'' to retain, it would likely be that one: shifting
from a robotic design based on \emph{modules and APIs} to a system based on
\emph{modules and human-level semantic interfaces} has been the main
facilitator both for glueing together heterogeneous deliberative modules in a
\emph{meaningful} way, and quickly developing prototypes for new
upper-cognition abilities, like natural dialogue and theory of mind.
